---
title: "Stroke Dataset"
author: "Hunter Blum, Ben Earnest, Andrew Pak Kim"
date: "3/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dataset:

https://www.kaggle.com/datasets/fedesoriano/stroke-prediction-dataset

# Libraries
```{r}
library(tidyverse)
library(caret)
library(NeuralNetTools)
library(nnet)

set.seed(123)
```

# Data
```{r}
Stroke <- read.csv("stroke.csv")
```

# Cleaning the Data

The data is pretty clean after running this code. All variables are the correct type after running it. The only variable missing data is BMI, which only has 200/5100 observations missing. 

## Structure
```{r}
str(Stroke)

#Get rid of one other observation in gender
Stroke <- Stroke %>% filter(gender!="Other")

#Fix specific variables
Stroke$hypertension <- as.factor(Stroke$hypertension)
Stroke$heart_disease <- as.factor(Stroke$heart_disease)
Stroke$bmi <- as.numeric(Stroke$bmi)
Stroke$stroke <- as.factor(Stroke$stroke)

#Make all character variables into factors
Stroke[sapply(Stroke, is.character)] <- lapply(Stroke[sapply(Stroke, is.character)], as.factor)


str(Stroke)

#Rename Factors for Easier Understanding
levels(Stroke$hypertension) <- c("No", "Yes")
levels(Stroke$heart_disease) <- c("No", "Yes")
levels(Stroke$stroke) <- c("No", "Yes")

#Get Rid of id
Stroke$id <- NULL
```
## NAs
```{r}
Stroke %>% 
  select(everything()) %>% 
  summarise_all(funs(sum(is.na(.))))
#Just 201 missing observations in bmi 

#We'll just delete the NAs for now
Stroke_clean <- na.omit(Stroke)
```


# Exploratory Data Analysis

Our target feature is stroke, where 1 indicates that a stroke occurred. For any binary attributes 1 is always the variable occurred (eg. 1 for heart disease means the patient had heart disease). 

## Dataset Overview
```{r}
summary(Stroke_clean)
head(Stroke_clean)
```

## Variable by Stroke
### Make Functions
```{r}
#Categorical
Cat_eda <- function(x, y) {
  p1 <- ggplot(Stroke_clean, aes(x={{x}})) + geom_bar(aes(fill=stroke) , color = "black") + ggtitle(paste0("Stroke with Respect to ", y)) + xlab(y) + ylab("Count")

  p2 <- ggplot(Stroke_clean, aes(x={{x}})) + geom_bar(aes(fill=stroke), position = "fill", color = "black") + ggtitle(paste0("Stroke with Respect to ",y, " (Normalized)")) + xlab(y) + ylab("Count")
  
  plot(p1)
  plot(p2)
}

#Numeric
Num_eda <- function(x, y) {
  p1 <- ggplot(Stroke_clean, aes(x={{x}})) +        geom_histogram(aes(fill=stroke), color = "black") +
    ggtitle(paste0("Stroke with Respect to ", y)) + xlab(y) + ylab("Count")

 p2 <- ggplot(Stroke_clean, aes(x={{x}})) +
   geom_histogram(aes(fill=stroke), color = "black", position =      "fill") +
   ggtitle(paste0("Stroke with Respect to ", y)) + xlab(y) +         ylab("Count")
 
 plot(p1)
 plot(p2)
  
}

```


### Categorical Variables
```{r}
Cat_eda(gender, "Gender")
Cat_eda(hypertension, "Hypertension")
Cat_eda(heart_disease, "Heart Disease")
Cat_eda(ever_married, "Ever Married")
Cat_eda(work_type, "Work Type")
Cat_eda(Residence_type, "Residence Type")
Cat_eda(smoking_status, "Smoking Status")
```

### Numeric variables
```{r}
Num_eda(age, "Age")
Num_eda(avg_glucose_level, "Avg. Glucose Level")
Num_eda(bmi, "BMI")
```

# Modelling 
## Partition Data & Create Folds for Cross-validation
```{r}
#Partition Data
trainIndex <- createDataPartition(y=Stroke_clean$stroke, p=0.8, list = F, times = 1)

Stroke_train <- Stroke_clean[trainIndex, ]
Stroke_test <- Stroke_clean[-trainIndex, ]

#Creating folds for 5-fold cross-validation
train <- createFolds(Stroke_clean$stroke, k=5)
```

# C5.0
##



# CART


# Logistic Regression


# Random Forest


# Naive Bayes


# Neural Network


# Association Rule



## Trying out ANN just to see how it works
```{r}
nnet_stroke <- train(stroke ~., method = "nnet", data = Stroke_clean, tuneLength = 5, 
                     trControl = trainControl(
                       method = "cv", index = train),
                trace = FALSE)     
                     )

nnet_stroke
plotnet(nnet_stroke$finalModel)
```
